---
title: "Recommendation"
author: "Merint"
date: "11/4/2019"
output: html_document
---

```{r}
library("recommenderlab")
library("ggplot2")
library(tidyverse)
library(cartography)
library(MASS)
library(ISLR)
library(rgdal)
library(dbplyr)
library(arules)
library(stringr)
```
```{r}
data(MovieLense)
class(MovieLense)

```

```{r}
dim(MovieLense)
slotNames(MovieLense)
```

```{r}
Data<- MovieLense@data
```

```{r}
ratings <- as.vector(Data)
unique(ratings)
```

```{r}
table_ratings <- table(ratings)
table_ratings
```

```{r}
ratings <- ratings[ratings != 0]
table(ratings)
```

```{r}
plot1<- qplot(ratings) + ggtitle("Number of Ratings")
plot1 + stat_bin(binwidth = 0.5, drop = FALSE, right = FALSE, col = "blue")
```



```{r}
avg_ratings <- colMeans(MovieLense)
qplot(avg_ratings) + stat_bin(binwidth = 0.5) +
ggtitle("Distribution of the average movie rating")
```

As we see, there are only a few count on ratings 1 and 5. This is coz very few people have rated these movies. We can put a threshold value of 100 here.

```{r}
avg_ratings_threshold <- avg_ratings[colCounts(MovieLense) > 100]

qplot(avg_ratings_threshold) + stat_bin(binwidth = 0.1) +
ggtitle("Distribution of average ratings with Threshold of 100")
```

Selecting only most relevant data. i.e users who have rated more than 50 movies and movies that have atleast 70 ratings

```{r}
Data_rel <- MovieLense[rowCounts(MovieLense)>50, colCounts(Data_rel)>70]
Data_rel
```

We now look at the rating distribution per user wise
```{r}
Avg_user_rat<- rowMeans(Data_rel)
qplot(Avg_user_rat, xlab="Average Ratings", ylab="Count") + stat_bin(binwidth = 0.1) +
ggtitle("Distribution of the average rating per user") 
```


Building recommender model using recommenderlab


Setiing a threshold value for good ratings
```{r}
thresh_ratings<- 3
```

Splitting the data
```{r}
split_sets<- evaluationScheme(data = Data_rel, method = "split", train = 0.75, given = 15, goodRating = thresh_ratings, k = 1)

split_sets
```

```{r}
Known <- getData(split_sets, "known")
Known
```
````{r}
Unknown<- getData(split_sets, "unknown")
Unknown
```

```{r}
Train <- getData(split_sets, "train")
Train
```


Training the recommender model for Item based Collaborative filtering
```{r}
recommender_model <- Recommender(data = Train, method = "IBCF", parameter = NULL)
```

```{r}
model_pred <- predict(object = recommender_model, newdata = Known, n = 10, type = "topNList")
```

```{r}
slotNames(model_pred)
```

```{r}
user1 <- model_pred@items[[5]]
pred_user1 <- model_pred@itemLabels[user1]
pred_user1
```


```{r}
model_accuracy<- calcPredictionAccuracy(x = model_pred, data = Unknown)
model_accuracy
```

Using Cross validation to find accuracy based on Users

```{r}
split_sets_CV<- evaluationScheme(data = Data_rel, method = "cross-validation", given = 15, goodRating = thresh_ratings, k = 5)
Known_CV <- getData(split_sets_CV, "known")
Unknown_CV <- getData(split_sets_CV, "unknown")
Train_CV <- getData(split_sets_CV, "train")
```
```{r}
Unknown_CV
```
 Item Based Collaborative filtering on CV sets
```{r}
recommender_model_IBCF_CV <- Recommender(data = Train_CV, method = "IBCF", parameter = NULL)
model_pred_IBCF_CV <- predict(object = recommender_model_IBCF_CV, newdata = Known_CV, n = 10, type = "ratings")
```

```{r}
model_accuracy_IBCF_CV<- calcPredictionAccuracy(x = model_pred_IBCF_CV, data = Unknown_CV, byUser=TRUE)
model_accuracy_IBCF_CV
```

```{r}
IBCF_Accuracy<- data.frame(model_accuracy_IBCF_CV)
hist(IBCF_Accuracy$RMSE, breaks=12, col="red", xlab="RMSE range", ylab="Count")
```


Now we follow the same for User based Collaborative filtering and also by varying the models wit different distance calculations. i.e Cosine, Pearson, and Euclidean.

Let's start IBCF with Pearsons
```{r}
recommender_model_IBCF_Pear <- Recommender(data = Train, method = "IBCF", param = list(method ="pearson"))
model_pred_IBCF_Pear <- predict(object = recommender_model_IBCF_Pear, newdata = Known, n = 10, type = "ratings")
model_accuracy_IBCF_Pear<- calcPredictionAccuracy(x = model_pred_IBCF_Pear, data = Unknown)
model_accuracy_IBCF_Pear
```

Next IBCF with Euclidean
```{r}
recommender_model_IBCF_Euc <- Recommender(data = Train, method = "IBCF", param = list(method ="Euclidean"))
model_pred_IBCF_Euc <- predict(object = recommender_model_IBCF_Euc, newdata = Known, n = 10, type = "ratings")
model_accuracy_IBCF_Euc<- calcPredictionAccuracy(x = model_pred_IBCF_Euc, data = Unknown)
model_accuracy_IBCF_Euc
```

Now we will calculater the UBCF with Cosine
```{r}
recommender_model_UBCF_Cos <- Recommender(data = Train, method = "UBCF", param = list(method ="cosine"))
model_pred_UBCF_Cos <- predict(object = recommender_model_UBCF_Cos, newdata = Known, n = 10, type = "ratings")
model_accuracy_UBCF_Cos<- calcPredictionAccuracy(x = model_pred_UBCF_Cos, data = Unknown)
model_accuracy_UBCF_Cos
```

Next UBCF with Pearsons
```{r}
recommender_model_UBCF_Pear <- Recommender(data = Train, method = "UBCF", param = list(method ="pearson"))
model_pred_UBCF_Pear <- predict(object = recommender_model_UBCF_Pear, newdata = Known, n = 10, type = "ratings")
model_accuracy_UBCF_Pear<- calcPredictionAccuracy(x = model_pred_UBCF_Pear, data = Unknown)
model_accuracy_UBCF_Pear
```

Now UBCF with Euclidean
```{r}
recommender_model_UBCF_Euc <- Recommender(data = Train, method = "UBCF", param = list(method ="Euclidean"))
model_pred_UBCF_Euc <- predict(object = recommender_model_UBCF_Euc, newdata = Known, n = 10, type = "ratings")
model_accuracy_UBCF_Euc<- calcPredictionAccuracy(x = model_pred_UBCF_Euc, data = Unknown)
model_accuracy_UBCF_Euc
```

```{r}
MSE<- c(model_accuracy[2],model_accuracy_IBCF_Euc[2], model_accuracy_IBCF_Pear[2],model_accuracy_UBCF_Cos[2],model_accuracy_UBCF_Euc[2],model_accuracy_UBCF_Pear[2])
```

```{r}
Models<- c("IBCF_C","IBCF_E","IBCF_P","UBCF_C","UBCF_E","UBCF_P")
```

```{r}
b<-barplot(MSE,names.arg=Models,xlab="Model types",ylab="MSE",col="yellow",
main="Recommender Model Comparison",border="red")
text(b, 0, round(MSE, 3),cex=1,pos=3)
```


Applying Apriori Algorithm

To begin with, we will binarize the data by keepting threshold rating as 3

```{r}
Data_bin <- binarize(MovieLense, minRating= thresh_ratings)
class(Data_bin)
```

Converting BinaryRatingMatrix to matrix
```{r}
Data_bin_matrix<- as(Data_bin,"matrix")
view(Data_bin_matrix)
```

Converting the TRUE and FALSE to 1s and 0s
```{r}
Data_bin_new<- 1*Data_bin_matrix
View(Data_bin_new)
```

Applying Apriori Algorithm
```{r}
rules <- apriori(data = Data_bin_new, parameter = list(supp =0.2, conf = 0.9))
```



```{r}
rules_df<- as(rules, "data.frame")
rules_df<-rules_df[order(-rules_df$lift, -rules_df$confidence), ]
```


